\section{Related Work}

\textbf{Video Visualization} Creating new visual representations from an input video to reveal important features and events in the video is a long-standing research problem. There is a large body of work that aims to automatically summarize videos to facilitate navigation and browsing. Recent survey papers \cite{truong2007video,borgo2011survey} comprehensively review these techniques, which can be broadly divided into two classes according to their output: \textit{video skims} and \textit{still-image abstracts}. Video skims \cite{he1999auto,ekin2003automatic,ngo2005video,lu2013story} summarize a longer video with a shorter video, usually consisting of segments extracted from the original video. These skims have the advantage of retaining audio and motion elements that is especially useful for expressing dynamic scenes, but they are less suitable for conveying dense, static information and still rely on timeline-based navigation. Still-image based methods \cite{uchihashi1999video,barnes2010video,hwang2006cinema,boreczky2000interactive}
primarily focus on conveying the visual content of a
video in static form through a collection of salient images extracted from the video. Most relevant to our work is \cite{choudary2007summarization}, which summarizes blackboard-style lectures by creating a panoramic frame of the board.

\textbf{Video Navigation Interface}
\cite{kim2014data} uses interaction data collected from MOOC platforms to introduce a set of techniques that augment existing video interface widgets. \cite{pavel2014video} provides a tool to create \texit{video digests}, structured summaries of informational videos organized into chapters and sections. 
Most closely related to our work is the NoteVideo interface by \cite{monserrat2013notevideo}, which presents a summarized image of the video composed of clickable visual links to specific places in  lecture.

\textbf{Improving Transcripts / Subtitles}
\cite{hu2015speaker} optimizing subtitle placement by speaker recognition. \cite{kurlander1996comic}, \cite{chun2006automated} subtitle placement for single frame in comic style cinema.



