\documentclass{report}
\begin{document}
\textbf{List of online-educational videos watched:}
\begin{enumerate}
\item EdX 6.041x: Introduction to Probability
\begin{itemize}
\item Highlighting visual parts that correspond to the audio script. Analog of laser pointer or indicator.
\item When complete slides are shown from the onset, making them appear in sequence as the topic is dealt with.
\item EdX: already cut into short sections with interspersed exercises. Could we do this for longer videos automatically?
\item How to fast forward visual--drawing or writing takes more time than audio so instructor inserts unnecessary remarks or slows down.
\item Without audio or script no idea to tell which part of slide the video is on (e.g. 6.041x, unit 3, unit 4 lec.5)
\end{itemize}

\item EdX: CS-184.1x Foundations of Computer Graphics
\begin{itemize}
\item Some slides could be better if combined (e.g. when it is under same title (continued...), chunks of code cut for space reasons--lecture 6, video 2)
\item Making links in the slides clickable (e.g. Ravi's homeapge)
\item Link the exercise questions to relevant parts of the lecture so that students can go back to find information specific to the question.
\end{itemize}

\item KhanAcademy: Differential Equation
\begin{itemize}
\item Remove useless parts of script, or rate them by importance. Visuals tend to be stationary when instructor is bantering.
\item Drawing arbitrary borders on blackboard instead of having discrete slides
\item Usually the instructor reads aloud what he is writing, and this is transcribed in the script. This may be useful to automatically change handwriting to typewrite.
\item Scrolling down board occludes "current relevant parts"
\end{itemize}

\item Khan Academy: Spring potential energy example 
\begin{itemize}
\item Important explanation is not necessarily written on board, but it is in transcript.
\item Also the spatial layout of the board is not sequential (left to right, or top to bottom)
\item Cut into sections the visual parts, and rearrange. Allowing copies.
\item Correcting mistake.
\end{itemize}

\item Udacity: Intro to Haddop and MapReduce
\begin{itemize}
\item Lecture is sectioned into multiple videos with different topics. On the top of the video there is a bar to choose sections titles. Something similar, where the time line is sectioned into parts of lectures would be useful. (e.g. explanation of potential energy, example problem etc.)
\item Transparent hand with pointer.
\item They built in problems inside lecture! And it gave feedback on the right hand side. This seemed to be not part of the video, but a web layer on top of the video.
\end{itemize}
\end{enumerate}

\textbf{General ideas:}
\begin{enumerate}
\item Difficult to define the problem: I keep wanting to improve the lecture content, slides.
\item Putting in headshot, when available when nothing interesting is happening in the visual slide (e.g. tv news)
\item Augmenting script with slide titles.
\item Categorize the script by importance: e.g. passing comment, examples, definition etc.
\item Where do students want to refer to? Which parts of lectures are most repeatedly watched?
\item Scope of problem: Which techniques can be applied generally, and which are type specific?
\end{enumerate}
\end{document}